Digital Twins for Ocean Robots

### 2024-06-19 paper/paper.tex
Update paper.tex
try half of .bib
rm accents in ref.bib

In the {\it digital twins for ocean robots} framework (DTOR), interactivity is facilitated by Julia and its large ecosystem of software packages. In particular, \pkg{Makie.jl} \cite{Makie} and \pkg{Pluto.jl} \cite{Pluto} let us operate even complex modeling workflows from notebooks and apps. The tutorial examples in \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, \pkg{ClimateModels.jl}, and \pkg{MITgcm.jl} \cite{Forget2024b} are notably available as Pluto notebooks. Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, and so on. Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzède2017,Bittig2018}.

@@

%MITgcm : \cite{marshall1997fvi,camp-etal:04,HHG05,Forget2015a,Forget2024b}
%OCCA / ECCO : \cite{Forget2007,Forget2010,Forget2015a,FFL15,FP15,Forget2024b}
%More : \cite{Forget2021,Wu2022,OceananigansJOSS,Makie,Innes2018,Pluto}

>>>>

In the {\it digital twins for ocean robots} framework (DTOR), interactivity is facilitated by Julia and its large ecosystem of software packages. In particular, \pkg{Makie.jl} \cite{Makie} and \pkg{Pluto.jl} \cite{Pluto} let us operate even complex modeling workflows from notebooks and apps. The tutorial examples in \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, \pkg{ClimateModels.jl}, and \pkg{MITgcm.jl} \cite{Forget2024b} are notably available as Pluto notebooks. Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, and so on. Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzede2017,Bittig2018}.

@@
